---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
```{r}
data <- read.csv("UCI-electricity/UCI_data.csv")

# Display the first few rows of the data
head(data)

# Display the last few rows of the data
tail(data)

# Display the structure of the data
str(data)

library(striprtf)

# Specify the path to your RTF file
file_path <- "UCI-electricity/description.rtf"

# Read the RTF file
rtf_content <- read_rtf(file_path)

# Display the content
cat(rtf_content)

# Count of missing values in each column
colSums(is.na(data))

# Percentage of missing values in each column
colMeans(is.na(data)) * 100
```




```{r}
# Set up the plotting area for multiple plots
par(mfrow=c(3, 1), mar=c(4, 4, 2, 1), oma=c(0, 0, 2, 0))

# Plot the histograms for temperature variables
par(mfrow=c(2, 5))
hist(data$T1, main="Kitchen", xlab="T1 (Celsius)", col="blue")
hist(data$T2, main="Living Room", xlab="T2 (Celsius)", col="green")
hist(data$T3, main="Laundry Room", xlab="T3 (Celsius)", col="red")
hist(data$T4, main="Office Room", xlab="T4 (Celsius)", col="purple")
hist(data$T5, main="Bathroom", xlab="T5 (Celsius)", col="orange")
hist(data$T6, main="Outside North", xlab="T6 (Celsius)", col="yellow")
hist(data$T7, main="Ironing Room", xlab="T7 (Celsius)", col="pink")
hist(data$T8, main="Teenager Room 2", xlab="T8 (Celsius)", col="cyan")
hist(data$T9, main="Parents Room", xlab="T9 (Celsius)", col="brown")
hist(data$T_out, main="Outside Chievres", xlab="T_out (Celsius)", col="grey")

# Add an overall title for the temperature histograms
mtext("Histograms of Temperature Variables", outer = TRUE, line = -2, cex = 1.5)

# Plot the histograms for humidity variables
par(mfrow=c(2, 5))
hist(data$RH_1, main="Kitchen", xlab="RH_1 (%)", col="blue")
hist(data$RH_2, main="Living Room", xlab="RH_2 (%)", col="green")
hist(data$RH_3, main="Laundry Room", xlab="RH_3 (%)", col="red")
hist(data$RH_4, main="Office Room", xlab="RH_4 (%)", col="purple")
hist(data$RH_5, main="Bathroom", xlab="RH_5 (%)", col="orange")
hist(data$RH_6, main="Outside North", xlab="RH_6 (%)", col="yellow")
hist(data$RH_7, main="Ironing Room", xlab="RH_7 (%)", col="pink")
hist(data$RH_8, main="Teenager Room 2", xlab="RH_8 (%)", col="cyan")
hist(data$RH_9, main="Parents Room", xlab="RH_9 (%)", col="brown")
hist(data$RH_out, main="Outside Chievres", xlab="RH_out (%)", col="grey")

# Add an overall title for the humidity histograms
mtext("Histograms of Humidity Variables", outer = TRUE, line = -22, cex = 1.5)

# Plot the histograms for additional numerical variables
par(mfrow=c(2, 3))
hist(data$Press_mm_hg, main="Pressure (Chievres)", xlab="Press_mm_hg (mm Hg)", col="blue")
hist(data$Windspeed, main="Wind Speed (Chievres)", xlab="Windspeed (m/s)", col="green")
hist(data$Visibility, main="Visibility (Chievres)", xlab="Visibility (km)", col="red")
hist(data$Tdewpoint, main="Dewpoint (Chievres)", xlab="Tdewpoint (Celsius)", col="purple")
hist(data$rv1, main="Random Variable 1", xlab="rv1", col="orange")
hist(data$rv2, main="Random Variable 2", xlab="rv2", col="yellow")
hist(data$TARGET_energy, main="Energy Use (Wh)", xlab="TARGET_energy (Wh)", col="pink")

# Add an overall title for the additional numerical variable histograms
mtext("Histograms of Additional Numerical Variables", outer = TRUE, line = -42, cex = 1.5)
```

### Analysis of Temperature Variables

- **Kitchen (T1):** 
  - Distribution is approximately normal with a peak around 22°C.
  - Most values range between 18°C and 26°C, indicating a stable temperature range in the kitchen.

- **Living Room (T2):** 
  - Slightly right-skewed distribution with a peak around 21°C.
  - Values range from 16°C to 28°C, showing some variability but generally centered around comfortable room temperature.

- **Laundry Room (T3):**
  - Approximately normal distribution with a peak around 24°C.
  - Values range between 18°C and 30°C, suggesting consistent conditions.

- **Office Room (T4):**
  - Normal distribution with a peak around 21°C.
  - Values range between 16°C and 24°C, indicating good temperature control.

- **Bathroom (T5):**
  - Approximately normal distribution with a peak around 22°C.
  - Values range between 16°C and 24°C, suggesting stable temperature control.

- **Outside North (T6):**
  - Distribution is right-skewed with a peak around 10°C.
  - Values range from 0°C to 30°C, reflecting wider external temperature variations.

- **Ironing Room (T7):**
  - Approximately normal distribution with a peak around 21°C.
  - Values range between 16°C and 24°C, indicating consistent temperature.

- **Teenager Room 2 (T8):**
  - Normal distribution with a peak around 22°C.
  - Values range between 16°C and 24°C, showing consistent conditions.

- **Parents Room (T9):**
  - Approximately normal distribution with a peak around 21°C.
  - Values range from 16°C to 24°C, suggesting stable conditions.

- **Outside (Chievres, T_out):**
  - Right-skewed distribution with a peak around 10°C.
  - Values range from -5°C to 25°C, showing greater external temperature variation.


### Analysis of Humidity Variables

- **Kitchen (RH_1):**
  - Normal distribution with a peak around 40%.
  - Values range between 30% and 50%, indicating stable humidity.

- **Living Room (RH_2):**
  - Normal distribution with a peak around 35%.
  - Values range between 20% and 40%, showing stable conditions.

- **Laundry Room (RH_3):**
  - Normal distribution with a peak around 40%.
  - Values range between 30% and 50%, suggesting consistent conditions.

- **Office Room (RH_4):**
  - Normal distribution with a peak around 35%.
  - Values range between 25% and 45%, indicating stable humidity.

- **Bathroom (RH_5):**
  - Right-skewed distribution with a peak around 60%.
  - Values range between 40% and 80%, reflecting variability.

- **Outside North (RH_6):**
  - Bi-modal distribution with peaks around 15% and 80%.
  - Values range from 0% to 100%, reflecting external humidity variability.

- **Ironing Room (RH_7):**
  - Normal distribution with a peak around 35%.
  - Values range between 25% and 45%, indicating consistent conditions.

- **Teenager Room 2 (RH_8):**
  - Normal distribution with a peak around 45%.
  - Values range between 30% and 60%, showing stable humidity.

- **Parents Room (RH_9):**
  - Normal distribution with a peak around 45%.
  - Values range from 30% to 50%, suggesting stable conditions.

- **Outside (Chievres, RH_out):**
  - Right-skewed distribution with a peak around 80%.
  - Values range from 20% to 100%, reflecting greater external humidity variation.

### Analysis of Additional Numerical Variables

- **Pressure (Chievres):**
  - Approximately normal distribution with a peak around 760 mm Hg.
  - Values range between 730 mm Hg and 770 mm Hg, indicating stable atmospheric pressure.

- **Wind Speed (Chievres):**
  - Right-skewed distribution with a peak around 2 m/s.
  - Values range from 0 to 14 m/s, reflecting variability in wind speed.

- **Visibility (Chievres):**
  - Bi-modal distribution with peaks around 30 km and 40 km.
  - Values range from 0 to 70 km, showing variability in visibility.

- **Dewpoint (Chievres):**
  - Approximately normal distribution with a peak around 5°C.
  - Values range between -5°C and 15°C, indicating variability in dew point.

- **Random Variable 1 (rv1):**
  - Uniform distribution across the range.
  - Values range between 0 and 50, suggesting a random distribution.

- **Random Variable 2 (rv2):**
  - Uniform distribution across the range.
  - Values range between 0 and 50, suggesting a random distribution.

- **Energy Use (Wh):**
  - Right-skewed distribution with a peak around 50 Wh.
  - Values range from 0 to 800 Wh, showing variability in energy usage.


```{r Critical Analysis}
# Compute the correlation matrix
cor_matrix <- cor(data[, sapply(data, is.numeric)], use="complete.obs")

# Install and load the corrplot package
install.packages("corrplot")
library(corrplot)

# Visualize the correlation matrix
corrplot(cor_matrix, method="circle", tl.cex = 0.5, tl.col = "black", tl.srt = 45)

```
## Correlation Analysis

The correlation matrix plot above visualizes the relationships between the numerical variables in the dataset. Here are the key observations:

- **Strong Positive Correlations:**
  - **T1, T2, T3, T4, T5, T7, T8, T9:** These temperature variables are strongly positively correlated with each other (correlation coefficients close to 1). This indicates that temperatures across different rooms in the house tend to increase and decrease together.
  - **RH_1, RH_2, RH_3, RH_4, RH_5, RH_7, RH_8, RH_9:** These humidity variables are also strongly positively correlated with each other, suggesting that humidity levels across different rooms tend to move in tandem.

- **Negative Correlations:**
  - **T1 and RH_1, T2 and RH_2, etc.:** There are moderate to strong negative correlations between temperature and humidity in the same room, indicating that as temperature increases, humidity decreases, and vice versa.

- **External Temperature (T_out):**
  - **T_out and T1, T2, etc.:** External temperature (T_out) has moderate positive correlations with internal temperatures, suggesting that changes in external temperature influence internal temperatures.

- **Pressure (Press_mm_hg):**
  - **Pressure and Humidity:** There is a slight negative correlation between pressure and humidity levels (RH_out), indicating that higher pressure may be associated with lower humidity levels.

- **Wind Speed (Windspeed):**
  - **Windspeed and Temperature:** Wind speed shows slight negative correlations with internal temperatures, suggesting that higher wind speeds might slightly reduce indoor temperatures.

- **Visibility:**
  - **Visibility and External Variables:** Visibility shows slight positive correlations with external temperature and slight negative correlations with external humidity.

- **Energy Use (TARGET_energy):**
  - **TARGET_energy and Internal Variables:** Energy use shows weak to moderate positive correlations with internal temperatures (e.g., T1, T2) and negative correlations with internal humidity levels (e.g., RH_1, RH_2). This indicates that higher energy use is associated with higher temperatures and lower humidity levels.

These observations provide insights into how different environmental variables interact within the house and with external conditions. The correlations between temperatures, humidity, and energy use can help in understanding the energy dynamics and potential factors influencing energy consumption in the house.


```{r Pair Plots}
# Install necessary packages if not already installed
install.packages("GGally")
install.packages("dplyr")

# Load the packages
library(GGally)
library(dplyr)

# Select the columns for temperature, humidity, and additional numerical variables
temperature_vars <- data %>% select(T1, T2, T3, T4, T5, T6, T7, T8, T9, T_out)
humidity_vars <- data %>% select(RH_1, RH_2, RH_3, RH_4, RH_5, RH_6, RH_7, RH_8, RH_9, RH_out)
additional_vars <- data %>% select(Press_mm_hg, Windspeed, Visibility, Tdewpoint, rv1, rv2, TARGET_energy)

# Create pair plot for temperature variables
ggpairs(temperature_vars, title = "Pair Plot for Temperature Variables")

# Create pair plot for humidity variables
ggpairs(humidity_vars, title = "Pair Plot for Humidity Variables")

# Create pair plot for additional numerical variables
ggpairs(additional_vars, title = "Pair Plot for Additional Numerical Variables")


```

```{r Outlier Detection}
# Box plots for temperature variables
par(mfrow=c(2, 5)) # Arrange plots in a 2x5 grid
boxplot(data$T1, main="Kitchen", col="blue")
boxplot(data$T2, main="Living Room", col="green")
boxplot(data$T3, main="Laundry Room", col="red")
boxplot(data$T4, main="Office Room", col="purple")
boxplot(data$T5, main="Bathroom", col="orange")
boxplot(data$T6, main="Outside North", col="yellow")
boxplot(data$T7, main="Ironing Room", col="pink")
boxplot(data$T8, main="Teenager Room 2", col="cyan")
boxplot(data$T9, main="Parents Room", col="brown")
boxplot(data$T_out, main="Outside (Chievres)", col="grey")

# Box plots for humidity variables
par(mfrow=c(2, 5)) # Arrange plots in a 2x5 grid
boxplot(data$RH_1, main="Kitchen", col="blue")
boxplot(data$RH_2, main="Living Room", col="green")
boxplot(data$RH_3, main="Laundry Room", col="red")
boxplot(data$RH_4, main="Office Room", col="purple")
boxplot(data$RH_5, main="Bathroom", col="orange")
boxplot(data$RH_6, main="Outside North", col="yellow")
boxplot(data$RH_7, main="Ironing Room", col="pink")
boxplot(data$RH_8, main="Teenager Room 2", col="cyan")
boxplot(data$RH_9, main="Parents Room", col="brown")
boxplot(data$RH_out, main="Outside (Chievres)", col="grey")

```


```{r Time Series Analysis}
install.packages("ggplot2")
install.packages("dplyr")
install.packages("tidyr")

# Load the packages
library(ggplot2)
library(dplyr)
library(tidyr)

# Convert the 'date' column to datetime format
data$date <- as.POSIXct(data$date, format="%Y-%m-%d %H:%M:%S")

# Create long format for temperature variables
temperature_vars <- data %>%
  select(date, T1, T2, T3, T4, T5, T6, T7, T8, T9, T_out) %>%
  pivot_longer(cols = -date, names_to = "variable", values_to = "value")

# Plot time series for temperature variables
ggplot(temperature_vars, aes(x=date, y=value, color=variable)) +
  geom_line() +
  labs(title="Temperature Time Series", y="Temperature (Celsius)", x="Date") +
  theme_minimal() +
  theme(legend.position="bottom") +
  scale_color_manual(values=c("blue", "green", "red", "purple", "orange", "yellow", "pink", "cyan", "brown", "grey"))

# Create long format for humidity variables
humidity_vars <- data %>%
  select(date, RH_1, RH_2, RH_3, RH_4, RH_5, RH_6, RH_7, RH_8, RH_9, RH_out) %>%
  pivot_longer(cols = -date, names_to = "variable", values_to = "value")

# Plot time series for humidity variables
ggplot(humidity_vars, aes(x=date, y=value, color=variable)) +
  geom_line() +
  labs(title="Humidity Time Series", y="Humidity (%)", x="Date") +
  theme_minimal() +
  theme(legend.position="bottom") +
  scale_color_manual(values=c("blue", "green", "red", "purple", "orange", "yellow", "pink", "cyan", "brown", "grey"))

# Plot time series for energy use
ggplot(data, aes(x=date, y=TARGET_energy)) +
  geom_line(color="blue") +
  labs(title="Energy Use Time Series", y="Energy Use (Wh)", x="Date") +
  theme_minimal()

```
### 1 Humidity Time Series

#### Critical Analysis

The humidity time series plot above visualizes the variations in humidity levels across different rooms and the outside environment over time. Here are the key observations:

- **High Variability:**
  - **RH_out:** There are significant fluctuations in the outside humidity levels, with frequent spikes and dips, indicating variable weather conditions.
  - **RH_1 to RH_9:** Humidity levels inside the house are relatively stable, suggesting effective climate control.

- **Patterns:**
  - **RH_5 and RH_7:** Certain rooms show different humidity patterns, which could be due to localized factors like the presence of water sources or ventilation differences.
  - **Indoor vs. Outdoor:** The stability of indoor humidity compared to outdoor suggests good insulation and effective use of HVAC systems.

### 2. Temperature Time Series

#### Critical Analysis

The temperature time series plot above visualizes the variations in temperature levels across different rooms and the outside environment over time. Here are the key observations:

- **Seasonal Patterns:**
  - **T_out:** External temperature shows clear seasonal patterns, with temperatures fluctuating more significantly during certain periods.
  - **T1 to T9:** Indoor temperatures remain relatively stable, indicating effective temperature control within the house.

- **Room Variability:**
  - **T3, T5:** Some rooms show more variability in temperature, potentially due to their location within the house or varying usage patterns.

- **Insulation Effect:**
  - The difference between indoor and outdoor temperature patterns suggests good insulation, which helps in maintaining a stable indoor environment despite external temperature changes.

### 3. Energy Use Time Series

#### Critical Analysis

The energy use time series plot above visualizes the variations in energy consumption over time. Here are the key observations:

- **High Variability:**
  - Energy use shows significant fluctuations, with frequent spikes that likely correspond to peak usage times or specific high-energy activities.

- **Cyclical Patterns:**
  - There appears to be a cyclical pattern in energy use, potentially corresponding to daily or weekly usage cycles, indicating regular consumption behaviors.

- **Peak Usage:**
  - The spikes in energy use highlight peak consumption periods, which could be targeted for energy-saving measures to improve overall efficiency.

### Conclusion

The time series plots provide valuable insights into the behavior of humidity, temperature, and energy use in the building. Understanding these patterns is crucial for developing predictive models and implementing energy-saving measures.

Further analysis could include:

- Correlating temperature and humidity with energy use to identify key drivers.
- Exploring anomalies and outliers to improve the reliability of the predictive models.
- Implementing feature engineering techniques to capture seasonal and cyclical patterns effectively.

By leveraging these insights, we can develop robust models to predict energy use and optimize energy consumption in low-energy buildings.

