### Rationale Behind Our Feature Engineering and Feature Importance Evaluation

Feature engineering and evaluating feature importance are critical steps in building a robust predictive model. Here’s a detailed explanation of why we performed these steps and the complete code to achieve them.

#### Rationale

1. **Feature Engineering:**
   - **Time-based Features:** Adding features like the hour of the day, day of the week, and month helps capture temporal patterns in energy usage.
   - **Lagged Features:** Including previous time steps’ energy usage can capture temporal dependencies.
   - **Rolling Statistics:** Calculating rolling means and standard deviations helps capture short-term trends and variability.
   - **Interaction Features:** Interaction terms between temperature and humidity can capture combined effects that are not evident when considering each variable independently.
   - **Polynomial Features:** Polynomial transformations help capture non-linear relationships between features and the target variable.
   - **Day/Night Indicator:** Adding a binary indicator for day and night can help model different energy usage patterns during these periods.

2. **Feature Importance Evaluation:**
   - **Random Forest Model:** Using a Random Forest model helps assess the importance of each feature based on how much they reduce the impurity in the trees. This provides insights into which features are most predictive of the target variable.

### Complete Code Implementation

#### Step 1: Install and Load Necessary Libraries

```{r}
# Install and load necessary libraries
install.packages("randomForest")
install.packages("ggplot2")
install.packages("caret")
install.packages("dplyr")
install.packages("zoo")

library(randomForest)
library(ggplot2)
library(caret)
library(dplyr)
library(zoo)
```

#### Step 2: Load and Prepare Data

We assume `data` is already loaded and `TARGET_energy` is the target variable.

```{r}
# Convert the 'date' column to datetime format
data$date <- as.POSIXct(data$date, format="%Y-%m-%d %H:%M:%S")

# Add Time-based Features
data$hour <- as.integer(format(data$date, "%H"))
data$day_of_week <- as.integer(format(data$date, "%u"))
data$month <- as.integer(format(data$date, "%m"))
```

#### Step 3: Feature Engineering

```{r}
# Add Lagged Features
data <- data %>%
  mutate(
    TARGET_energy_lag1 = lag(TARGET_energy, 1),
    TARGET_energy_lag24 = lag(TARGET_energy, 24)
  )

# Add Rolling Statistics
data <- data %>%
  mutate(
    TARGET_energy_rollmean_3 = rollmean(TARGET_energy, 3, fill = NA, align = "right"),
    TARGET_energy_rollsd_3 = rollapply(TARGET_energy, 3, sd, fill = NA, align = "right"),
    T1_rollmean_3 = rollmean(T1, 3, fill = NA, align = "right"),
    T1_rollsd_3 = rollapply(T1, 3, sd, fill = NA, align = "right")
  )

# Add Interaction Features
data <- data %>%
  mutate(
    T1_RH1_interaction = T1 * RH_1,
    T2_RH2_interaction = T2 * RH_2,
    T3_RH3_interaction = T3 * RH_3,
    T4_RH4_interaction = T4 * RH_4,
    T5_RH5_interaction = T5 * RH_5,
    T6_RH6_interaction = T6 * RH_6,
    T7_RH7_interaction = T7 * RH_7,
    T8_RH8_interaction = T8 * RH_8,
    T9_RH9_interaction = T9 * RH_9
  )

# Add Polynomial Features
data <- data %>%
  mutate(
    T1_squared = T1^2,
    RH1_squared = RH_1^2,
    T1_cubed = T1^3,
    RH1_cubed = RH_1^3,
    T2_squared = T2^2,
    RH2_squared = RH_2^2,
    T2_cubed = T2^3,
    RH2_cubed = RH_2^3,
    T3_squared = T3^2,
    RH3_squared = RH_3^2,
    T3_cubed = T3^3,
    RH3_cubed = RH_3^3,
    T4_squared = T4^2,
    RH4_squared = RH_4^2,
    T4_cubed = T4^3,
    RH4_cubed = RH_4^3,
    T5_squared = T5^2,
    RH5_squared = RH_5^2,
    T5_cubed = T5^3,
    RH5_cubed = RH_5^3,
    T6_squared = T6^2,
    RH6_squared = RH_6^2,
    T6_cubed = T6^3,
    RH6_cubed = RH_6^3,
    T7_squared = T7^2,
    RH7_squared = RH_7^2,
    T7_cubed = T7^3,
    RH7_cubed = RH_7^3,
    T8_squared = T8^2,
    RH8_squared = RH_8^2,
    T8_cubed = T8^3,
    RH8_cubed = RH_8^3,
    T9_squared = T9^2,
    RH9_squared = RH_9^2,
    T9_cubed = T9^3,
    RH9_cubed = RH_9^3
  )

# Add Day/Night Indicator
data <- data %>%
  mutate(
    is_day = ifelse(hour >= 6 & hour < 18, 1, 0)
  )

# Check for missing values in the engineered data
colSums(is.na(data))

# Handle missing values (if any) by removing them
data <- na.omit(data)
```

#### Step 4: Evaluate Feature Importance Using Random Forest

```{r}
# Split the cleaned data into training and testing sets
set.seed(123)
trainIndex <- createDataPartition(data$TARGET_energy, p = .8, 
                                  list = FALSE, 
                                  times = 1)
trainData <- data[trainIndex,]
testData <- data[-trainIndex,]

# Ensure the target variable is numeric
trainData$TARGET_energy <- as.numeric(trainData$TARGET_energy)
testData$TARGET_energy <- as.numeric(testData$TARGET_energy)

# Train a Random Forest model
set.seed(2024)
rf_model <- randomForest(TARGET_energy ~ ., data = trainData, importance = TRUE, ntree = 100)

# Print the model summary
print(rf_model)

# Get feature importance
importance <- importance(rf_model)
importance_df <- data.frame(Feature = rownames(importance), Importance = importance[,1])

# Sort by importance
importance_df <- importance_df[order(-importance_df$Importance), ]

# Plot feature importance
ggplot(importance_df, aes(x = reorder(Feature, Importance), y = Importance)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  theme_minimal() +
  labs(title = "Feature Importance", x = "Feature", y = "Importance")

# Save the plot as a bigger image
ggsave("feature_importance.png", width = 18, height = 20)

```

### Summary

By following these steps, we can effectively engineer features based on domain knowledge and insights from the data. Evaluating feature importance using a Random Forest model helps us identify the most predictive features, thereby simplifying the model and potentially improving its performance. This comprehensive approach ensures that we leverage all relevant information from the data to build a robust predictive model.